---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---


## Loading and preprocessing the data
Loading data here:
```{r loadingdata, echo=TRUE}
activitydata <- read.csv('activity.csv',na.strings="NA", sep=',')
collectdates <- as.Date(activitydata$date, format='%Y-%m-%d')

```

## What is mean total number of steps taken per day?

```{r meansteps, echo=TRUE}
library(dplyr)

tabledata <- tbl_df(activitydata)
groupdata <- group_by(tabledata, date)
meansteps <- summarize(groupdata, sum(steps))
hist(meansteps$sum)

mstep <- mean(meansteps$sum)
mestep <- median(meansteps$sum)

```
The mean number of steps taken per day is 'r mstep'.
The median number of steps taken per day is 'r mestep'.

## What is the average daily activity pattern?

```{r totoalsteps, echo=TRUE}
stepsvsinterval <- aggregate(steps~ interval, tabledata, mean)

with(stepsvsinterval, plot(interval, steps, type='l', xlab=interval, ylab='average steps'))

```
maxsteps <- which.max(stepsvsinterval$steps)
maxinterval <- stepsvsinterval[maxsteps,1]

At 'r maxinterval' of the 5-minute intervals, the maximum number of steps is found.

## Imputing missing values

```{r missingvalues, echo=TRUE}
missrows <- is.na(tabledata$steps)
totalmissingvalue <- sum(missrows)

newtable <- tabledata
newtable[missrows, 1] <- mean(meansteps$sum)

hist(newtable$steps)

```

## Are there differences in activity patterns between weekdays and weekends?


